\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-10 manuscript.Rmd
* attempt 1 on solving systemfonts pack issue
Updated ReadME

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex

mainfont: Helvetica
---

@@

```{r depMan, eval=FALSE, include=FALSE}
renv::init()
renv::snapshot()
Nrenv::status()
renv::restore()
```

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "Supplymentary.Rmd"
  - "instrument.Rmd"
  - "Appendix-B.Rmd"
mainfont: Helvetica
---

@@

```{r depMan, eval=FALSE, include=FALSE}
#renv::init()
#renv::snapshot()
#renv::status()
#renv::restore()
```

### 2021-11-10 manuscript.tex
Updated ReadME

\begin{verbatim}
## * The library is already synchronized with the lockfile.
\end{verbatim}

@@

\begin{tabular}{llllll}
\toprule
 & \multicolumn{1}{c}{a} & \multicolumn{1}{c}{b1} & \multicolumn{1}{c}{b2} & \multicolumn{1}{c}{b3} & \multicolumn{1}{c}{b4}\\
\midrule
item16 & 28.13 & 0.78 & 0.90 & 1.06 & 1.40\\
item36 & 4.49 & 0.94 & 1.08 & 1.23 & 1.40\\
item17 & 2.81 & 0.97 & 1.11 & 1.38 & 1.62\\
item11 & 3.27 & -0.79 & 0.65 & 1.54 & 2.31\\
item10 & 3.07 & -1.27 & -0.09 & 0.82 & 2.00\\
item12 & 1.72 & -0.67 & 0.44 & 1.28 & 2.11\\
item7 & 1.09 & -0.50 & 0.73 & 1.63 & 2.97\\
Ritem8 & 1.19 & -2.26 & -0.48 & 0.64 & 1.91\\
item9 & 0.91 & -2.63 & -0.96 & 1.11 & 3.49\\
item27 & 2.21 & -1.88 & -1.19 & -0.73 & 0.30\\
item3 & 3.03 & -1.24 & -0.77 & -0.20 & 0.66\\
item40 & 1.55 & -0.51 & 0.46 & 1.32 & 2.22\\
item30 & 0.49 & 3.27 & 3.74 & 4.64 & 6.52\\
item41 & 0.51 & 3.87 & 4.78 & 6.39 & 8.91\\
item32 & 1.62 & -1.03 & -0.78 & -0.42 & 0.16\\
item35 & 1.37 & -1.09 & -0.98 & -0.75 & -0.40\\
item38 & 0.40 & -7.48 & -5.56 & -4.23 & -0.90\\
item33 & 12.31 & -0.66 & -0.48 & -0.24 & 0.13\\
item46 & 2.22 & 0.68 & 0.89 & 1.38 & 2.17\\
item45 & 1.51 & 0.30 & 0.55 & 1.17 & 1.91\\
item25 & 0.52 & -1.37 & -0.04 & 1.89 & 4.22\\
item4 & 0.84 & 2.44 & 2.80 & 3.18 & 3.67\\
item1 & 0.39 & -0.91 & 1.52 & 3.25 & 5.53\\
\bottomrule
\addlinespace
\end{tabular}

@@

>>>>

@@

\begin{tabular}{llllll}
\toprule
 & \multicolumn{1}{c}{a} & \multicolumn{1}{c}{b1} & \multicolumn{1}{c}{b2} & \multicolumn{1}{c}{b3} & \multicolumn{1}{c}{b4}\\
\midrule
item16 & 28.55 & 0.78 & 0.90 & 1.06 & 1.40\\
item36 & 4.49 & 0.94 & 1.08 & 1.23 & 1.40\\
item17 & 2.81 & 0.97 & 1.11 & 1.38 & 1.62\\
item11 & 3.27 & -0.79 & 0.65 & 1.54 & 2.31\\
item10 & 3.07 & -1.27 & -0.09 & 0.82 & 2.00\\
item12 & 1.72 & -0.67 & 0.44 & 1.28 & 2.11\\
item7 & 1.09 & -0.50 & 0.73 & 1.63 & 2.97\\
Ritem8 & 1.19 & -2.26 & -0.48 & 0.64 & 1.91\\
item9 & 0.91 & -2.63 & -0.96 & 1.11 & 3.49\\
item27 & 2.21 & -1.88 & -1.19 & -0.73 & 0.30\\
item3 & 3.03 & -1.24 & -0.77 & -0.20 & 0.66\\
item40 & 1.55 & -0.51 & 0.46 & 1.32 & 2.22\\
item30 & 0.49 & 3.27 & 3.74 & 4.64 & 6.52\\
item41 & 0.51 & 3.87 & 4.78 & 6.39 & 8.91\\
item32 & 1.62 & -1.03 & -0.78 & -0.42 & 0.16\\
item35 & 1.36 & -1.09 & -0.98 & -0.75 & -0.40\\
item38 & 0.40 & -7.50 & -5.58 & -4.25 & -0.91\\
item33 & 13.51 & -0.66 & -0.48 & -0.24 & 0.13\\
item46 & 2.22 & 0.68 & 0.89 & 1.38 & 2.17\\
item45 & 1.51 & 0.30 & 0.55 & 1.17 & 1.91\\
item25 & 0.52 & -1.37 & -0.04 & 1.89 & 4.22\\
item4 & 0.84 & 2.44 & 2.80 & 3.18 & 3.67\\
item1 & 0.39 & -0.91 & 1.52 & 3.25 & 5.53\\
\bottomrule
\addlinespace
\end{tabular}

@@

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\begin{table}[tbp]

\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}

\begin{tabular}{cccccccc}
\toprule
item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
item16 & 1 &  &  &  &  & 0.996 & 0.004\\
item36 & 0.94 &  &  &  &  & 0.897 & 0.103\\
item17 & 0.8 &  &  &  &  & 0.658 & 0.342\\
item11 &  & 0.79 &  &  &  & 0.642 & 0.358\\
item10 &  & 0.76 &  &  &  & 0.592 & 0.408\\
item12 &  & 0.65 &  &  &  & 0.465 & 0.535\\
item7 &  & 0.5 &  &  &  & 0.267 & 0.733\\
item8 &  & -0.49 &  &  &  & 0.252 & 0.748\\
item9 &  & 0.32 &  &  &  & 0.113 & 0.887\\
item27 &  &  & 0.8 &  &  & 0.659 & 0.341\\
item3 &  &  & 0.8 &  &  & 0.683 & 0.317\\
item40 &  &  & 0.65 &  &  & 0.464 & 0.536\\
item30 &  &  & 0.45 &  &  & 0.353 & 0.647\\
item41 &  &  & 0.36 &  &  & 0.329 & 0.671\\
item33 &  &  &  & 0.74 &  & 0.555 & 0.445\\
item32 &  &  &  & 0.73 &  & 0.623 & 0.377\\
item35 &  &  &  & 0.66 &  & 0.455 & 0.545\\
item37 &  &  &  & -0.39 &  & 0.175 & 0.825\\
item38 &  &  &  & 0.38 &  & 0.178 & 0.822\\
item46 &  &  &  &  & 0.6 & 0.422 & 0.578\\
item45 &  &  &  &  & 0.59 & 0.374 & 0.626\\
item25 &  &  &  &  & 0.41 & 0.193 & 0.807\\
item4 &  &  &  &  & 0.41 & 0.219 & 0.781\\
item1 &  &  &  &  & 0.4 & 0.17 & 0.83\\
item26 &  &  &  &  & 0.35 & 0.165 & 0.835\\
\% of Variance & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 &  & \\
\bottomrule
\addlinespace
\end{tabular}

\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
item19 & 1.78 &  &  &  &  &  & 3.318 & -2.318\\
item5 &  &  &  &  &  &  & 0.11 & 0.89\\
item16 &  & 1 &  &  &  &  & 1.004 & -0.004\\
item36 &  & 0.91 &  &  &  &  & 0.86 & 0.14\\
item17 &  & 0.81 &  &  &  &  & 0.691 & 0.309\\
item11 &  &  & 0.83 &  &  &  & 0.71 & 0.29\\
item10 &  &  & 0.79 &  &  &  & 0.638 & 0.362\\
item12 &  &  & 0.63 &  &  &  & 0.465 & 0.535\\
item8 &  &  & -0.5 &  &  &  & 0.269 & 0.731\\
item7 &  &  & 0.47 &  &  &  & 0.268 & 0.732\\
item9 &  &  & 0.32 &  &  &  & 0.163 & 0.837\\
item33 &  &  &  & 0.83 &  &  & 0.698 & 0.302\\
item32 &  &  &  & 0.75 &  &  & 0.666 & 0.334\\
item35 &  &  &  & 0.64 &  &  & 0.446 & 0.554\\
item31 &  &  &  & 0.48 &  &  & 0.331 & 0.669\\
item38 &  &  &  & 0.39 &  &  & 0.191 & 0.809\\
item37 &  &  &  & -0.35 &  &  & 0.153 & 0.847\\
item3 &  &  &  &  & 0.85 &  & 0.748 & 0.252\\
item27 &  &  &  &  & 0.8 &  & 0.644 & 0.356\\
item40 &  &  &  &  & 0.68 &  & 0.507 & 0.493\\
item46 &  &  &  &  &  & 0.6 & 0.431 & 0.569\\
item45 &  &  &  &  &  & 0.56 & 0.341 & 0.659\\
item4 &  &  &  &  &  & 0.43 & 0.265 & 0.735\\
item25 &  &  &  &  &  & 0.4 & 0.178 & 0.822\\
item1 &  &  &  &  &  & 0.36 & 0.142 & 0.858\\
item26 &  &  &  &  &  & 0.36 & 0.173 & 0.827\\
item13 &  &  &  &  &  &  & 0.087 & 0.913\\
item29 &  &  &  &  &  &  & 0.108 & 0.892\\
\% of Variance & 0.12 & 0.09 & 0.09 & 0.08 & 0.07 & 0.06 &  & \\
\bottomrule
\addlinespace
\end{tabular}

\end{table}
\end{appendix}

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today)
and still a work in progress. Please do not distribute!

LEBA captures light exposure-related behaviours on a 5 point Likert type
scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely
= 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is
calculated by the summation of scores of items belonging to the
corresponding factor. The following instruction is given before
displaying the items: ``Please indicate how often you performed the
following behaviours in the past 4 weeks.''

\blandscape

\hypertarget{leba-long-form-23-items}{%
\section{LEBA Long Form (23 Items)}\label{leba-long-form-23-items}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Items
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Never/Does not apply/I don't know
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Rarely
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Sometimes
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Often
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Always
\end{minipage} \\
\midrule
\endhead
1 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
indoors during the day. & & & & & \\
2 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
outdoors during the day. & & & & & \\
3 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
within 1 hour before attempting to fall asleep. & & & & & \\
4 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
5 & I spend between 1 and 3 hours per day (in total) outside. & & & &
& \\
6 & I spend between 30 minutes and 1 hour per day (in total) outside. &
& & & & \\
7 & I spend more than 3 hours per day (in total) outside. & & & & & \\
8 & I spend as much time outside as possible. & & & & & \\
9 & I go for a walk or exercise outside within 2 hours after waking up.
& & & & & \\
10 & I use my mobile phone within 1 hour before attempting to fall
asleep. & & & & & \\
11 & I look at my mobile phone screen immediately after waking up. & & &
& & \\
12 & I check my phone when I wake up at night. & & & & & \\
13 & I look at my smartwatch within 1 hour before attempting to fall
asleep. & & & & & \\
14 & I look at my smartwatch when I wake up at night. & & & & & \\
15 & I dim my mobile phone screen within 1 hour before attempting to
fall asleep. & & & & & \\
16 & I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. & & & & & \\
17 & I use as little light as possible when I get up during the night. &
& & & & \\
18 & I dim my computer screen within 1 hour before attempting to fall
asleep. & & & & & \\
19 & I use tunable lights to create a healthy light environment. & & & &
& \\
20 & I use LEDs to create a healthy light environment. & & & & & \\
21 & I use a desk lamp when I do focused work. & & & & & \\
22 & I use an alarm with a dawn simulation light. & & & & & \\
23 & I turn on the lights immediately after waking up. & & & & & \\
\bottomrule
\end{longtable}

\elandscape

\blandscape

\hypertarget{latent-structure-reliability-and-structural-validity}{%
\subsection{Latent Structure, Reliability and Structural
Validity}\label{latent-structure-reliability-and-structural-validity}}

The long form of LEBA consists 23 items with five factors.

Factor names

Items

Reliability Coefficients

McDonald's Omega

(N=262)

Reliability Coefficients

Cronbach's alpha

F1: Wearing blue light filters

1-3

.93

.90

F2: Spending time outdoors

4-9 (Item 4 is reversed)

.80

.78

F3: Using phone and smartwatch in bed

10-14

.61

.62

F4: Using light before bedtime

15-18

.72

.62

F5: Using light in the morning and during daytime

19-23

.45

.41

.73(Total scale)

LEBA -long form showed satisfactory structural validity (CFI =.97; TLI =
.96; RMSEA = .05{[}.04-.06, 90\% CI{]}; SRMR = .09).

\hypertarget{how-to-cite}{%
\subsection{How to cite:}\label{how-to-cite}}

\elandscape

\blandscape

\hypertarget{leba-short-form-17-items}{%
\section{LEBA Short Form (17 Items)}\label{leba-short-form-17-items}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Short Form (17 Items)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Never/Does not apply/I don't know
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Rarely
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Sometimes
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Often
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Always
\end{minipage} \\
\midrule
\endhead
01 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
indoors during the day. & & & & & \\
02 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
outdoors during the day. & & & & & \\
03 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
within 1 hour before attempting to fall asleep. & & & & & \\
04 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
05 & I spend between 1 and 3 hours per day (in total) outside. & & & &
& \\
06 & I spend more than 3 hours per day (in total) outside. & & & & & \\
07 & I spend as much time outside as possible. & & & & & \\
08 & I go for a walk or exercise outside within 2 hours after waking up.
& & & & & \\
09 & I use my mobile phone within 1 hour before attempting to fall
asleep. & & & & & \\
10 & I look at my mobile phone screen immediately after waking up. & & &
& & \\
11 & I check my phone when I wake up at night. & & & & & \\
12 & I dim my mobile phone screen within 1 hour before attempting to
fall asleep. & & & & & \\
13 & I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. & & & & & \\
14 & I dim my computer screen within 1 hour before attempting to fall
asleep. & & & & & \\
15 & I use tunable lights to create a healthy light environment. & & & &
& \\
16 & I use LEDs to create a healthy light environment. & & & & & \\
17 & I use an alarm with a dawn simulation light. & & & & & \\
\bottomrule
\end{longtable}

\elandscape

\blandscape

\hypertarget{latent-structure-reliability-and-structural-validity-1}{%
\subsection{Latent Structure, Reliability and Structural
Validity}\label{latent-structure-reliability-and-structural-validity-1}}

The short form of LEBA consists 23 items with five factors.

\begin{longtable}[]{@{}ll@{}}
\toprule
Factor names & Items \\
\midrule
\endhead
\textbf{F1: Wearing blue light filters} & 1-3 \\
\textbf{F2: Spending time outdoors} & 4-8 (Item 4 is reversed) \\
\textbf{F3: Using phone and smart-watch in bed} & 9-11 \\
\textbf{F4: Using light before bedtime} & 12-14 \\
\textbf{F5: Using light in the morning and during daytime} & 15-17 \\
\bottomrule
\end{longtable}

\hypertarget{how-to-cite-1}{%
\subsection{How to cite:}\label{how-to-cite-1}}

\elandscape
\end{appendix}

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\hypertarget{supplimentary-analysis}{%
\subsection{Supplimentary Analysis}\label{supplimentary-analysis}}

\begin{table}[h]

\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}

\begin{tabular}{ccccccc}
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
Item2 & 2.76 & 1.75 & -0.10 & -1.42 & 0.88* & .20\\
Item3 & 3.34 & 1.43 & -0.58 & -0.77 & 0.88* & .18\\
Item4 & 1.30 & 1.31 & 1.93 & 2.92 & 0.62* & .32\\
Item5 & 3.95 & 1.56 & -1.42 & 0.75 & 0.70* & .19\\
Item6 & 2.70 & 1.66 & 0.02 & -1.33 & 0.90* & .18\\
Item7 & 2.23 & 1.28 & 0.60 & -0.59 & 0.89* & .18\\
Item8 & 2.95 & 1.24 & -0.19 & -0.70 & 0.93* & -.07\\
Item9 & 2.92 & 1.09 & -0.37 & 0.11 & 0.91* & .14\\
Item10 & 2.73 & 1.07 & -0.03 & -0.52 & 0.92* & .27\\
Item11 & 2.17 & 0.93 & 0.44 & 0.20 & 0.89* & .25\\
Item12 & 2.34 & 1.26 & 0.46 & -0.58 & 0.91* & .24\\
Item13 & 2.71 & 1.49 & 0.14 & -1.29 & 0.89* & .28\\
Item14 & 2.11 & 1.34 & 0.68 & -0.78 & 0.84* & .24\\
Item15 & 3.26 & 1.11 & -0.34 & -0.21 & 0.91* & .11\\
Item16 & 1.46 & 1.31 & 1.71 & 1.90 & 0.65* & .33\\
Item17 & 1.43 & 1.30 & 1.76 & 2.12 & 0.64* & .30\\
Item18 & 0.92 & 0.67 & 2.00 & 9.41 & 0.62* & .32\\
Item19 & 0.85 & 0.56 & 1.71 & 10.74 & 0.55* & .34\\
Item20 & 0.83 & 0.54 & 1.76 & 13.92 & 0.53* & .31\\
Item21 & 0.94 & 0.75 & 2.46 & 10.66 & 0.58* & .27\\
Item22 & 3.57 & 1.08 & -0.72 & 0.08 & 0.88* & .19\\
Item23 & 2.53 & 1.31 & 0.22 & -0.91 & 0.92* & .11\\
Item24 & 4.13 & 1.01 & -1.39 & 2.01 & 0.78* & .19\\
Item25 & 2.57 & 1.43 & 0.22 & -1.23 & 0.88* & .17\\
Item26 & 2.23 & 1.30 & 0.59 & -0.63 & 0.88* & .16\\
Item27 & 3.78 & 1.34 & -1.01 & 0.08 & 0.82* & .18\\
Item28 & 3.75 & 1.16 & -0.78 & -0.10 & 0.86* & .01\\
Item29 & 2.38 & 1.40 & 0.20 & -1.04 & 0.92* & .11\\
Item30 & 0.94 & 1.42 & 1.66 & 1.69 & 0.68* & .24\\
Item31 & 2.91 & 1.76 & -0.24 & -1.41 & 0.87* & .45\\
Item32 & 3.49 & 1.76 & -0.71 & -1.06 & 0.78* & .43\\
Item33 & 3.56 & 1.75 & -0.79 & -0.95 & 0.77* & .32\\
Item34 & 3.30 & 2.00 & -0.54 & -1.50 & 0.74* & .34\\
Item35 & 3.80 & 1.79 & -1.07 & -0.59 & 0.67* & .24\\
Item36 & 1.36 & 1.38 & 1.75 & 2.05 & 0.65* & .38\\
Item37 & 1.30 & 0.94 & 2.79 & 7.65 & 0.48* & -.01\\
Item38 & 4.27 & 1.18 & -2.07 & 4.01 & 0.65* & .23\\
Item39 & 1.94 & 1.01 & 0.85 & 0.61 & 0.86* & .05\\
Item40 & 2.13 & 1.24 & 0.56 & -0.54 & 0.89* & .16\\
Item41 & 0.87 & 1.08 & 1.68 & 2.74 & 0.73* & .21\\
Item42 & 3.90 & 1.55 & -1.15 & -0.12 & 0.72* & .17\\
Item43 & 1.59 & 1.23 & 1.59 & 1.70 & 0.69* & .22\\
Item44 & 3.46 & 1.41 & -0.92 & -0.01 & 0.86* & .38\\
Item45 & 2.04 & 1.66 & 0.46 & -1.12 & 0.87* & .29\\
Item46 & 1.57 & 1.40 & 0.97 & -0.07 & 0.82* & .38\\
Item47 & 2.07 & 1.23 & 0.59 & -0.42 & 0.89* & .34\\
Item48 & 2.57 & 1.30 & 0.14 & -0.74 & 0.93* & .31\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} *p<.001}
\end{tablenotes}

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}

\caption{Correlation plot of the items}\label{fig:figCorAppB}
\end{figure}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB}
\end{figure}

Horn's parallel analysis with 500 iterations indicated a five-factor
solution. However, Scree plot and the MAP method suggested 6-factor
solution. five-factor solution . As a result, we tested both five-factor
and six-factor solutions.

\begin{table}[h]

\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
item19 & 0.99 &  &  &  &  & 1.01 & -0.01 & 1.06\\
item20 & 0.91 &  &  &  &  & 0.87 & 0.13 & 1.11\\
item18 & 0.82 &  &  &  &  & 0.71 & 0.29 & 1.12\\
item21 & 0.8 &  &  &  &  & 0.68 & 0.32 & 1.16\\
item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.30\\
item11 &  & 0.83 &  &  &  & 0.69 & 0.31 & 1.01\\
item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.03\\
item12 &  & 0.56 &  &  &  & 0.37 & 0.63 & 1.37\\
item8 &  & -0.44 &  &  &  & 0.21 & 0.79 & 1.11\\
item7 &  & 0.42 &  &  &  & 0.23 & 0.77 & 1.61\\
item9 &  & 0.33 &  &  &  & 0.12 & 0.88 & 1.10\\
item16 &  &  & 0.95 &  &  & 0.95 & 0.05 & 1.10\\
item17 &  &  & 0.74 &  &  & 0.60 & 0.41 & 1.17\\
item36 & 0.3 &  & 0.73 &  &  & 0.65 & 0.35 & 1.43\\
item3 &  &  &  & 0.85 &  & 0.75 & 0.25 & 1.05\\
item27 &  &  &  & 0.78 &  & 0.62 & 0.38 & 1.03\\
item40 &  &  &  & 0.71 &  & 0.51 & 0.49 & 1.05\\
item35 &  &  &  &  & 0.58 & 0.35 & 0.65 & 1.09\\
item48 &  &  &  &  & 0.57 & 0.35 & 0.65 & 1.14\\
item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.08\\
item47 &  &  &  &  & 0.52 & 0.29 & 0.71 & 1.19\\
item44 &  &  &  &  & 0.45 & 0.22 & 0.78 & 1.15\\
item31 &  &  &  &  & 0.41 & 0.21 & 0.79 & 1.48\\
item38 &  &  &  &  & 0.33 & 0.13 & 0.87 & 1.32\\
\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 & NA & NA & NA\\
\bottomrule
\addlinespace
\end{tabular}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}
